Music Perception 2: Analysis

### 2022-10-14 experiment-1/analysis/analysis.Rmd
upload analysis summary to RPubs
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: 'Music Perception 1: Analysis'
output:
  html_document:
    df_print: paged
---

@@

qqnorm(ioi[Skill == "articulation"]$Teaching)
qqline(ioi[Skill == "articulation"]$Teaching)
ioi_art_norm_teaching

qqnorm(ioi[Skill == "articulation"]$Mean)
qqline(ioi[Skill == "articulation"]$Mean)
ioi_art_norm_performance

@@

qqnorm(ioi[Skill == "dynamics"]$Teaching)
qqline(ioi[Skill == "dynamics"]$Teaching)
ioi_dyn_norm_teaching

qqnorm(ioi[Skill == "dynamics"]$Mean)
qqline(ioi[Skill == "dynamics"]$Mean)
ioi_dyn_norm_performance

@@

qqnorm(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

qqnorm(ioi_tra[Skill == "articulation"]$Teaching)
qqline(ioi_tra[Skill == "articulation"]$Teaching)
ioi_art_tra_norm_teaching

qqnorm(ioi_tra[Skill == "articulation"]$Mean)
qqline(ioi_tra[Skill == "articulation"]$Mean)
ioi_art_tra_norm_performance

@@

qqnorm(ioi_tra[Skill == "dynamics"]$Teaching)
qqline(ioi_tra[Skill == "dynamics"]$Teaching)
ioi_dyn_tra_norm_teaching

qqnorm(ioi_tra[Skill == "dynamics"]$Mean)
qqline(ioi_tra[Skill == "dynamics"]$Mean)
ioi_dyn_tra_norm_performance

@@

qqnorm(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

qqnorm(cv[Skill == "articulation"]$Teaching)
qqline(cv[Skill == "articulation"]$Teaching)
cv_art_norm_teaching

qqnorm(cv[Skill == "articulation"]$CV)
qqline(cv[Skill == "articulation"]$CV)
cv_art_norm_performance

@@

qqnorm(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
qqline(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)

qqnorm(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$CV)
qqline(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$CV)

@@

qqnorm(cv[Skill == "dynamics"]$Teaching)
qqline(cv[Skill == "dynamics"]$Teaching)
cv_dyn_norm_teaching

qqnorm(cv[Skill == "dynamics"]$CV)
qqline(cv[Skill == "dynamics"]$CV)
cv_dyn_norm_performance

@@

qqnorm(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
qqline(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)

qqnorm(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
qqline(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)

@@

qqnorm(kot_all[Subcomponent == "Legato"]$Teaching)
qqline(kot_all[Subcomponent == "Legato"]$Teaching)
kot_leg_norm_teaching

qqnorm(kot_all[Subcomponent == "Legato"]$Mean)
qqline(kot_all[Subcomponent == "Legato"]$Mean)
kot_leg_norm_performance

@@

qqnorm(kot_all[Subcomponent == "Staccato"]$Teaching)
qqline(kot_all[Subcomponent == "Staccato"]$Teaching)
kot_sta_norm_teaching

qqnorm(kot_all[Subcomponent == "Staccato"]$Mean)
qqline(kot_all[Subcomponent == "Staccato"]$Mean)
kot_sta_norm_performance

@@

qqnorm(kot_all[Subcomponent == "Forte"]$Teaching)
qqline(kot_all[Subcomponent == "Forte"]$Teaching)
kot_for_norm_teaching

qqnorm(kot_all[Subcomponent == "Forte"]$Mean)
qqline(kot_all[Subcomponent == "Forte"]$Mean)
kot_for_norm_performance

@@

qqnorm(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

qqnorm(kot_all[Subcomponent == "Piano"]$Teaching)
qqline(kot_all[Subcomponent == "Piano"]$Teaching)
kot_pia_norm_teaching

qqnorm(kot_all[Subcomponent == "Piano"]$Mean)
qqline(kot_all[Subcomponent == "Piano"]$Mean)
kot_pia_norm_performance

@@

qqnorm(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

qqnorm(vel_all[Subcomponent == "Forte"]$Teaching)
qqline(vel_all[Subcomponent == "Forte"]$Teaching)
vel_for_norm_teaching

qqnorm(vel_all[Subcomponent == "Forte"]$Mean)
qqline(vel_all[Subcomponent == "Forte"]$Mean)
vel_for_norm_performance

@@

qqnorm(vel_all[Subcomponent == "Piano"]$Teaching)
qqline(vel_all[Subcomponent == "Piano"]$Teaching)
vel_pia_norm_teaching

qqnorm(vel_all[Subcomponent == "Piano"]$Mean)
qqline(vel_all[Subcomponent == "Piano"]$Mean)
vel_pia_norm_performance

@@

qqnorm(vel_all[Subcomponent == "Legato"]$Teaching)
qqline(vel_all[Subcomponent == "Legato"]$Teaching)
vel_leg_norm_teaching

qqnorm(vel_all[Subcomponent == "Legato"]$Mean)
qqline(vel_all[Subcomponent == "Legato"]$Mean)
vel_leg_norm_performance

@@

qqnorm(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

qqnorm(vel_all[Subcomponent == "Staccato"]$Teaching)
qqline(vel_all[Subcomponent == "Staccato"]$Teaching)
vel_sta_norm_teaching

qqnorm(vel_all[Subcomponent == "Staccato"]$Mean)
qqline(vel_all[Subcomponent == "Staccato"]$Mean)
vel_sta_norm_performance

@@

qqnorm(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
qqline(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
vel_diff_ftop_norm_teaching

qqnorm(vel_diff_all[Subcomponent == "FtoP"]$Mean)
qqline(vel_diff_all[Subcomponent == "FtoP"]$Mean)
vel_diff_ftop_norm_performance

@@

qqnorm(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
qqline(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
vel_diff_ptof_norm_teaching

qqnorm(vel_diff_all[Subcomponent == "PtoF"]$Mean)
qqline(vel_diff_all[Subcomponent == "PtoF"]$Mean)
vel_diff_ptof_norm_performance

@@

qqnorm(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
qqline(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
vel_diff_ltos_norm_teaching

qqnorm(vel_diff_all[Subcomponent == "LtoS"]$Mean)
qqline(vel_diff_all[Subcomponent == "LtoS"]$Mean)
vel_diff_ltos_norm_performance

@@

qqnorm(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

qqnorm(vel_diff_all[Subcomponent == "StoL"]$Teaching)
qqline(vel_diff_all[Subcomponent == "StoL"]$Teaching)
vel_diff_stol_norm_teaching

qqnorm(vel_diff_all[Subcomponent == "StoL"]$Mean)
qqline(vel_diff_all[Subcomponent == "StoL"]$Mean)
vel_diff_stol_norm_performance

@@

## Legato
```{r, echo = FALSE}
m1 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Legato"])
summary(m1)
check_model(m1)
```

@@

## Staccato
```{r, echo = FALSE}
m2 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Staccato"])
summary(m2)
check_model(m2)
```

@@

## Forte
```{r, echo = FALSE}
m3 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Forte"])
summary(m3)
check_model(m3)
```

@@

## Piano
```{r, echo = FALSE}
m4 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Piano"])
summary(m4)
check_model(m4)
```

>>>>

---
title: 'Music Perception: Analysis (Experiment 1)'
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

# qqnorm(ioi[Skill == "articulation"]$Teaching)
# qqline(ioi[Skill == "articulation"]$Teaching)
# ioi_art_norm_teaching
# 
# qqnorm(ioi[Skill == "articulation"]$Mean)
# qqline(ioi[Skill == "articulation"]$Mean)
# ioi_art_norm_performance

@@

# qqnorm(ioi[Skill == "dynamics"]$Teaching)
# qqline(ioi[Skill == "dynamics"]$Teaching)
# ioi_dyn_norm_teaching
# 
# qqnorm(ioi[Skill == "dynamics"]$Mean)
# qqline(ioi[Skill == "dynamics"]$Mean)
# ioi_dyn_norm_performance

@@

# qqnorm(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# qqline(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# 
# qqnorm(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
# qqline(ioi[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

# qqnorm(ioi_tra[Skill == "articulation"]$Teaching)
# qqline(ioi_tra[Skill == "articulation"]$Teaching)
# ioi_art_tra_norm_teaching
# 
# qqnorm(ioi_tra[Skill == "articulation"]$Mean)
# qqline(ioi_tra[Skill == "articulation"]$Mean)
# ioi_art_tra_norm_performance

@@

# qqnorm(ioi_tra[Skill == "dynamics"]$Teaching)
# qqline(ioi_tra[Skill == "dynamics"]$Teaching)
# ioi_dyn_tra_norm_teaching
# 
# qqnorm(ioi_tra[Skill == "dynamics"]$Mean)
# qqline(ioi_tra[Skill == "dynamics"]$Mean)
# ioi_dyn_tra_norm_performance

@@

# qqnorm(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# qqline(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# 
# qqnorm(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
# qqline(ioi_tra[Skill == "dynamics" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

# qqnorm(cv[Skill == "articulation"]$Teaching)
# qqline(cv[Skill == "articulation"]$Teaching)
# cv_art_norm_teaching
# 
# qqnorm(cv[Skill == "articulation"]$CV)
# qqline(cv[Skill == "articulation"]$CV)
# cv_art_norm_performance

@@

# qqnorm(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
# qqline(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
# 
# qqnorm(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$CV)
# qqline(cv[Skill == "articulation" & CV > mean-2*sd & CV < mean+2*sd]$CV)

@@

# qqnorm(cv[Skill == "dynamics"]$Teaching)
# qqline(cv[Skill == "dynamics"]$Teaching)
# cv_dyn_norm_teaching
# 
# qqnorm(cv[Skill == "dynamics"]$CV)
# qqline(cv[Skill == "dynamics"]$CV)
# cv_dyn_norm_performance

@@

# qqnorm(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
# qqline(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$Teaching)
# 
# qqnorm(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)
# qqline(cv[Skill == "dynamics" & CV > mean-2*sd & CV < mean+2*sd]$CV)

@@

# qqnorm(kot_all[Subcomponent == "Legato"]$Teaching)
# qqline(kot_all[Subcomponent == "Legato"]$Teaching)
# kot_leg_norm_teaching
# 
# qqnorm(kot_all[Subcomponent == "Legato"]$Mean)
# qqline(kot_all[Subcomponent == "Legato"]$Mean)
# kot_leg_norm_performance

@@

# qqnorm(kot_all[Subcomponent == "Staccato"]$Teaching)
# qqline(kot_all[Subcomponent == "Staccato"]$Teaching)
# kot_sta_norm_teaching
# 
# qqnorm(kot_all[Subcomponent == "Staccato"]$Mean)
# qqline(kot_all[Subcomponent == "Staccato"]$Mean)
# kot_sta_norm_performance

@@

# qqnorm(kot_all[Subcomponent == "Forte"]$Teaching)
# qqline(kot_all[Subcomponent == "Forte"]$Teaching)
# kot_for_norm_teaching
# 
# qqnorm(kot_all[Subcomponent == "Forte"]$Mean)
# qqline(kot_all[Subcomponent == "Forte"]$Mean)
# kot_for_norm_performance

@@

# qqnorm(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# qqline(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# 
# qqnorm(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
# qqline(kot_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

# qqnorm(kot_all[Subcomponent == "Piano"]$Teaching)
# qqline(kot_all[Subcomponent == "Piano"]$Teaching)
# kot_pia_norm_teaching
# 
# qqnorm(kot_all[Subcomponent == "Piano"]$Mean)
# qqline(kot_all[Subcomponent == "Piano"]$Mean)
# kot_pia_norm_performance

@@

# qqnorm(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# qqline(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# 
# qqnorm(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
# qqline(kot_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

# qqnorm(vel_all[Subcomponent == "Forte"]$Teaching)
# qqline(vel_all[Subcomponent == "Forte"]$Teaching)
# vel_for_norm_teaching
# 
# qqnorm(vel_all[Subcomponent == "Forte"]$Mean)
# qqline(vel_all[Subcomponent == "Forte"]$Mean)
# vel_for_norm_performance

@@

# qqnorm(vel_all[Subcomponent == "Piano"]$Teaching)
# qqline(vel_all[Subcomponent == "Piano"]$Teaching)
# vel_pia_norm_teaching
# 
# qqnorm(vel_all[Subcomponent == "Piano"]$Mean)
# qqline(vel_all[Subcomponent == "Piano"]$Mean)
# vel_pia_norm_performance

@@

# qqnorm(vel_all[Subcomponent == "Legato"]$Teaching)
# qqline(vel_all[Subcomponent == "Legato"]$Teaching)
# vel_leg_norm_teaching
# 
# qqnorm(vel_all[Subcomponent == "Legato"]$Mean)
# qqline(vel_all[Subcomponent == "Legato"]$Mean)
# vel_leg_norm_performance

@@

# qqnorm(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# qqline(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# 
# qqnorm(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
# qqline(vel_all[Subcomponent == "Legato" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

# qqnorm(vel_all[Subcomponent == "Staccato"]$Teaching)
# qqline(vel_all[Subcomponent == "Staccato"]$Teaching)
# vel_sta_norm_teaching
# 
# qqnorm(vel_all[Subcomponent == "Staccato"]$Mean)
# qqline(vel_all[Subcomponent == "Staccato"]$Mean)
# vel_sta_norm_performance

@@

# qqnorm(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
# qqline(vel_diff_all[Subcomponent == "FtoP"]$Teaching)
# vel_diff_ftop_norm_teaching
# 
# qqnorm(vel_diff_all[Subcomponent == "FtoP"]$Mean)
# qqline(vel_diff_all[Subcomponent == "FtoP"]$Mean)
# vel_diff_ftop_norm_performance

@@

# qqnorm(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
# qqline(vel_diff_all[Subcomponent == "PtoF"]$Teaching)
# vel_diff_ptof_norm_teaching
# 
# qqnorm(vel_diff_all[Subcomponent == "PtoF"]$Mean)
# qqline(vel_diff_all[Subcomponent == "PtoF"]$Mean)
# vel_diff_ptof_norm_performance

@@

# qqnorm(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
# qqline(vel_diff_all[Subcomponent == "LtoS"]$Teaching)
# vel_diff_ltos_norm_teaching
# 
# qqnorm(vel_diff_all[Subcomponent == "LtoS"]$Mean)
# qqline(vel_diff_all[Subcomponent == "LtoS"]$Mean)
# vel_diff_ltos_norm_performance

@@

# qqnorm(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# qqline(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# 
# qqnorm(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
# qqline(vel_diff_all[Subcomponent == "LtoS" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

# qqnorm(vel_diff_all[Subcomponent == "StoL"]$Teaching)
# qqline(vel_diff_all[Subcomponent == "StoL"]$Teaching)
# vel_diff_stol_norm_teaching
# 
# qqnorm(vel_diff_all[Subcomponent == "StoL"]$Mean)
# qqline(vel_diff_all[Subcomponent == "StoL"]$Mean)
# vel_diff_stol_norm_performance

@@

## Legato
```{r, echo = FALSE, fig.height = 4}
m1 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Legato"])
summary(m1)
check_model(m1)
```

@@

## Staccato
```{r, echo = FALSE, fig.height = 4}
m2 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Staccato"])
summary(m2)
check_model(m2)
```

@@

## Forte
```{r, echo = FALSE, fig.height = 4}
m3 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Forte"])
summary(m3)
check_model(m3)
```

@@

## Piano
```{r, echo = FALSE, fig.height = 4}
m4 <- lm(Teaching ~ IOI + KOT + KV + KVDiff, data = partial[Subcomponent == "Piano"])
summary(m4)
check_model(m4)
```

### 2022-10-14 experiment-2/analysis/analysis.Rmd
upload analysis summary to RPubs
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

---
title: "Music Perception 2: Analysis"
output:
  html_document:
    df_print: paged
---

@@

qqnorm(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

qqnorm(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

qqnorm(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

qqnorm(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
qqline(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)

qqnorm(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
qqline(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

>>>>

---
title: "Music Perception 2: Analysis"
output:
  html_notebook: default
editor_options: 
  chunk_output_type: inline
---

@@

# qqnorm(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# qqline(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# 
# qqnorm(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
# qqline(vel_all[Subcomponent == "Forte" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

# qqnorm(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# qqline(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# 
# qqnorm(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
# qqline(vel_all[Subcomponent == "Piano" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

# qqnorm(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# qqline(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# 
# qqnorm(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
# qqline(vel_diff_all[Subcomponent == "FtoP" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)

@@

# qqnorm(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# qqline(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Teaching)
# 
# qqnorm(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
# qqline(vel_diff_all[Subcomponent == "PtoF" & Mean > mean-2*sd & Mean < mean+2*sd]$Mean)
